Model LF

### 2022-12-07 max_dp endogen stød.Rmd
commit

@@

>>>>

## Baseline Scenario 9 pp

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs9 <- list(

```{r}
# Simulate the model (following shock)
Shock_bs9 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs9
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs9 = Shock_bs9$simulation$max_dp
wage_bs9 = Shock_bs9$simulation$wage
komp_r_bs9 = Shock_bs9$simulation$komp_r
part_bs9 = Shock_bs9$simulation$part
yk_ds_bs9 = Shock_bs9$simulation$yk_ds
pc_ds_bs9 = Shock_bs9$simulation$pc_ds
wage_ds_t_bs9 = Shock_bs9$simulation$wage_ds_t
ur_ds_bs9 = Shock_bs9$simulation$ur_ds
emp_bs9 = Shock_bs9$simulation$emp
yd_hk_ds_bs9 = Shock_bs9$simulation$yd_hk_ds
prodk_bs9 = Shock_bs9$simulation$prodk
tilpas_pr_bs9 = Shock_bs9$simulation$tilpas_pr
u_ds_bs9 = Shock_bs9$simulation$u_ds
part_bs9 = Shock_bs9$simulation$part
nben_h_bs9 = Shock_bs9$simulation$nben_h
wage_ds_bs9 = Shock_bs9$simulation$wage_ds
dp_person_bs9 = Shock_bs9$simulation$dp_person
kont_h_ratio_bs9 = Shock_bs9$simulation$kont_h_ratio
lf_bs9 = Shock_bs9$simulation$lf
nl_g_bs9 = Shock_bs9$simulation$nl_g
unemp_bs9 = Shock_bs9$simulation$unemp
yd_hk_ds_bs9 = Shock_bs9$simulation$yd_hk_ds
wage_gap1_bs9 = Shock_bs9$simulation$wage_gap1
wage_gap_bs9 = Shock_bs9$simulation$wage_gap
prod_bs9 = Shock_bs9$simulation$prod
ur_test_bs9 = Shock_bs9$simulation$ur_test
ur_bs9 = Shock_bs9$simulation$ur
y_bs9 = Shock_bs9$simulation$y
yk_bs9 = Shock_bs9$simulation$yk
```

@@

# Scenario 9 pp

```{r}
# Define add-factor list (defining shock)
constantAdjList9 <- list(

```{r}
# Simulate the model (following shock)
Shock_9 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList9
                    )

yk_ds_09 = Shock_9$simulation$yk_ds
emp_09 = Shock_9$simulation$emp
wage_ds_09= Shock_9$simulation$wage_ds
ur_ds_09 = Shock_9$simulation$ur_ds
pc_ds_09 = Shock_9$simulation$pc_ds
yd_hk_ds_09 = Shock_9$simulation$yd_hk_ds
pconk_ds_09 = Shock_9$simulation$pconk_ds
komp_r_09 = Shock_9$simulation$komp_r
max_dp_09 = Shock_9$simulation$max_dp
nben_h_09 = Shock_9$simulation$nben_h
yd_hk_ds_09 = Shock_9$simulation$yd_hk_ds
ik_09 = Shock_9$simulation$ik
wage_ds_t_09 = Shock_9$simulation$wage_ds_t
nben_h_un_09 = Shock_9$simulation$nben_h_un
nl_g_09 = Shock_9$simulation$nl_g
nsben_h_09 = Shock_9$simulation$nsben_h
dp_person_09 = Shock_9$simulation$dp_person
u_ds_09 = Shock_9$simulation$u_ds
shock_kuld_09 = Shock_9$simulation$shock_kuld
unemp_09 = Shock_9$simulation$unemp
lf_09 = Shock_9$simulation$lf
part_09 = Shock_9$simulation$part
yk_09 = Shock_9$simulation$yk
y_09 = Shock_9$simulation$y
prodk_09 = Shock_9$simulation$prodk
```

plot(((wage_ds_t_09 - wage_ds_t_bs9) / wage_ds_t_bs9)*100, col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()
